Thermodynamic fragments for magic states in quantum computation

### 2021-03-21 appendix.tex
restructuring

%%%

@@

Similarly, not all stochastic matrices correspond to completely positive operations.
As an example, consider the permutation matrix
\begin{equation}
    \Pi_X = \begin{psmallmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0
    \end{psmallmatrix} \otimes \begin{psmallmatrix}
        0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0    
    \end{psmallmatrix} \in \stochw,\ d=5.
\end{equation}
It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive operation.

@@

In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
\end{align}
where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Similarly, not all stochastic matrices correspond to completely positive operations.
As an example, consider the permutation matrix
\begin{equation}
    \Pi_X = \begin{psmallmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0
    \end{psmallmatrix} \otimes \begin{psmallmatrix}
        0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0    
    \end{psmallmatrix} \in {\rm{S}}_5({\W{\frac{1}{5}\id}}).
\end{equation}
It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive (hence quantum) operation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\nick{In particular}, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
\end{align}
where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical details of bound derivation in stabiliser fragments}
\label{app:lcst_technical}
